Intelligent Quadcopter for IARC 2018

### 2018-06-01 IARC_Paper_2018/Paper.tex
Finishing touches on bibliography

\usepackage{graphicx,
			amssymb,
			amsmath,
			titlesec,
			lipsum,
			setspace,
			lastpage,
			fancyhdr,
			tikz,
			titling}
\usepackage{tkz-euclide}
\usepackage{setspace}

@@

%%%%%%%%%%%% SET AUTHOR NAMES AND AFFILIATIONS %%%%%%%%%%%%
\affiliatedauthor{Noel Brownback}{The University of Texas at Austin}
\affiliatedauthor{Anthony Carreon}{The University of Texas at Austin}
\affiliatedauthor{Shayer Hassan}{The University of Texas at Austin}
\affiliatedauthor{Eric Johnson}{The University of Texas at Austin}
\affiliatedauthor{Colin Lewis}{The University of Texas at Austin}
\affiliatedauthor{Mark Loveland}{The University of Texas at Austin}
\affiliatedauthor{Umer Salman}{The University of Texas at Austin}
\affiliatedauthor{Ethan Starr}{The University of Texas at Austin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\subsection*{Yearly Milestones}
	2017 - Have a working bot, with computer vision software in working or nearly working
	2018 - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, tweak the physique of the drone for better flight control and stability

@@

\section*{Payload}
	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, and array of cameras and 3 Nvidia Jetson TX2s. In addition the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter are a downwards-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.

@@

		\subsubsection*{Mission Sensors}
			For the goal of completing Mission 7 the drone must be able to detect Roombas and obstacles. The quadcopter is equipped with a single downward facing camera, four outward facing cameras, and a two-dimensional plane LiDAR sensor for obstacle avoidance.
			The singular bottom camera is a Logitech C210 webcam. This webcam is used for Roomba detection and tracking the targeted Roomba for autonomous interaction.For the four peripheral cameras are Logitech 960 C270. These are used to recognize and track the Roombas around the playing field. These five webcams provides enough information allowing the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
			The 2D LiDAR sensor is the SWEEP sensor by Scanse. This is a single LiDAR that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection. We chose to use this for obstacle detection rather than four separate LiDARs or webcams to save on computing power.

@@

				\textbf{Transformation}:

>>>>

\usepackage{graphicx,
			amssymb,
			amsmath,
			titlesec,
			lipsum,
			setspace,
			lastpage,
			fancyhdr,
			tikz,
			titling}
\usepackage{tkz-euclide}
\usepackage{setspace}
\usepackage{hyperref}

@@

%%%%%%%%%%%% SET AUTHOR NAMES AND AFFILIATIONS %%%%%%%%%%%%
\affiliatedauthor{Noel Brownback}{\vspace{-.5cm}}
\affiliatedauthor{Anthony Carreon}{\vspace{-.5cm}}
\affiliatedauthor{Shayer Hassan}{\vspace{-.5cm}}
\affiliatedauthor{Eric Johnson}{\vspace{-.5cm}}
\affiliatedauthor{Colin Lewis}{\vspace{-.5cm}}
\affiliatedauthor{Mark Loveland}{\vspace{-.5cm}}
\affiliatedauthor{Umer Salman}{\vspace{-.5cm}}
\affiliatedauthor{Ethan Starr}{The University of Texas at Austin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\subsection*{Yearly Milestones}

	2017 - Have a working bot, with computer vision software in working or nearly working

	2018 - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, tweak the physique of the drone for better flight control and stability

@@

\section*{Payload}
	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, and an array of cameras and 3 Nvidia Jetson TX2s. In addition the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter are: a downwards-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our Pixhawk 2 flight control board.

@@

		\subsubsection*{Mission Sensors}
			For the goal of completing Mission 7 the drone must be able to detect Roombas and obstacles. The quadcopter is equipped with a single downward facing camera and four outward facing cameras for image recognition, as well as a two-dimensional plane LiDAR sensor for obstacle avoidance.

			The singular bottom camera is a Logitech C210 webcam. This webcam is used for Roomba detection and tracking the targeted Roomba for autonomous interaction.For the four peripheral cameras are Logitech 960 C270. These are used to recognize and track the Roombas around the playing field. These five webcams provides enough information allowing the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
			The 2D LiDAR sensor is the SWEEP sensor by Scanse. This is a single LiDAR that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection. We chose to use this for obstacle detection rather than four separate LiDARs or webcams to save on computing power.

@@

			\pagebreak
				\textbf{Transformation}:
